Exploring the Evolution of Energy in Radiohead's Music

### 2024-11-21 paper/paper.qmd
Add comments in the scripts

---
title: "Exploring the Evolution of Energy in Radiohead's Music"
subtitle: "Energy Levels Fluctuate Post-2000 with Positive Correlations to Valence and Loudness Across Albums"
author: 
  - Yawen Tan
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Spotify-Data-Analysis/tree/main]"
date: today
date-format: long
abstract: "Radiohead's music shows notable variation in energy, valence, and loudness across their discography. This analysis examines the trends in energy levels over time, the distribution of energy across albums, and the relationships between energy, positivity, and loudness. The results indicate that energy levels fluctuate significantly around post-2000 and post-2015, with louder and more positive songs tending to have higher energy. Understanding these patterns provides insights into the band's evolving artistic approach and the diversity of their musical output."
format: pdf
number-sections: true
table-of-contents: true
bibliography: references.bib
---

>>>>

---
title: "Exploring the Evolution of Energy in Radiohead's Music"
subtitle: "Energy Levels Fluctuate Post-2000 with Positive Correlations to Valence and Loudness Across Albums"
author: 
  - Jianing Li
  - Xizi Sun
  - Yawen Tan
  - Shanjie Jiao
  - Xinqi Yue
  - Duanyi Su
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Spotify-Data-Analysis/tree/main]"
date: today
date-format: long
abstract: "Radiohead's music shows notable variation in energy, valence, and loudness across their discography. This analysis examines the trends in energy levels over time, the distribution of energy across albums, and the relationships between energy, positivity, and loudness. The results indicate that energy levels fluctuate significantly around post-2000 and post-2015, with louder and more positive songs tending to have higher energy. Understanding these patterns provides insights into the band's evolving artistic approach and the diversity of their musical output."
format: pdf
number-sections: true
table-of-contents: true
bibliography: references.bib
---
